The limits of self commitment and private paternalism \thanks{}

### 2020-08-14 main.tex
final edits to iv_pf table

 \documentclass[11pt]{article}

\input{preamble.tex}
\usepackage{anyfontsize}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

@@

\usepackage{lmodern} 
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\wh}{\widehat}
\onehalfspacing

\usepackage{comment}
\usepackage{subcaption,graphicx}

%para esconder columnas en tablas (enrique)
\usepackage{array}
\newcolumntype{H}{>{\setbox0=\hbox\bgroup}c<{\egroup}@{}}

@@

\pagenumbering{arabic}

@@

\section{Introduction}

@@

\newpage
\section{Experiment} \label{Experiment}

@@

Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client being a repeat costumer. We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75. We know its a different piece from it having a different weight/value.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract. This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only 16\% recover their piece in the fist 75 days in the fee forcing contract). The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar result. The third coefficient conditions on clients who recovered the pawn in both arms. The fourth coefficient focuses on the subsample who had or would have had a financial cost savings treatment effect above the median treatment effect in their first pawn. It shows that for these clients the likelihood of coming back is twice as large (although imprecise). That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment. We view these as suggestive correlations. The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix. %We also implemented an exit survey which clients filled when recovering their piece. Unfortunately it had low response rate (7\%), and we take its results with a grain of salt. In this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses. %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').  This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp. This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Figures}

\begin{figure}[H]
     \caption{Experiment description}
    \label{exp_description}
    \begin{center}
    \begin{subfigure}{.50\textwidth}
      \caption{Timeline of the experiment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
    \caption{Experiment arms}
       \centering
      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
    \end{subfigure}
    \end{center}
         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013. The gray lines arrows correspond to the dates of implementation of the experiment. We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs. Panel (b) shows our 5 treatment arms: control (status quo contract), no fee-forcing, promise-forcing, choice among status quo and fee-commitment, and choice among status quo promise-commitment. Within each arm it displays the number of observations. And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
\end{figure}

@@

% APPENDIX

\setcounter{table}{0}
\renewcommand{\thetable}{\thesection.\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{\thesection.\arabic{figure}}

\setcounter{section}{0}
\setcounter{subsection}{0}
\renewcommand\thesection{A\arabic{section}}
\renewcommand\thesubsection{\thesection\arabic{subsection}}

\appendix

\section{APPENDIX A}
\vspace{.2in}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}
\scriptsize{\input{./Tables/mechanism.tex}}
\end{center}
 \scriptsize
This table explores treatment effects in ``intermediate variables''. Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison. All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one. $R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6. The last row shows the mean of the dependent variable for the control group. Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done. Column (2) records the number of payments done within 230 days of the pawn. Column (3) is the average size of the payments for each client in pesos. Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch. Column (5) measures the number of days it took to recover the pawn, conditional on recovering. The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn. For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.

@@

\newpage
\subsection{FOSD: fee forcing vs status quo financial cost distributions}

@@

% APPENDIX B
\setcounter{table}{0}
\setcounter{figure}{0}

\newpage
\section{APPENDIX B: Observational analysis}
\label{appendix_b}
\vspace{.2in}
\normalsize

@@

\vspace{.1in}
\begin{figure}[H]
        \caption{Existence of FP per branch}
    \label{variation_pf_suc}
    \begin{center}
        \centering
        \includegraphics[width=\textwidth]{Figuras/active_pf_suc.pdf}
    \end{center}
     \scriptsize This Figure shows the presence of the frequent payment (FP) contract in 20 randomly chosen branches of Lender $P$ for a span of more than 4 years. A y value =1 means that in that month the FP contract was available in that branch. 
     %\textit{Do file: }  \texttt{active\_pf\_suc.do}
\end{figure}
\vspace{.1in}

@@

\vspace{.2in}
\begin{table}[H]
\caption{Experience with frequent payment contract raises future demand for it}
\label{iv_pf}
\begin{center}
\footnotesize{\input{./Tables/iv_reg_demand_pf.tex}}
\end{center}
 \scriptsize
This table shows resulting estimates of variants of equation  \ref{eqn:IV} above. They regress a dummy for the client choosing a frequent payment contract (when both the traditional one and the FP are available) on whether the previous loan was under a FP contract. All columns have client, branch, and calendar month fixed effects. All of them control for the number of times the client has pawned in the 12 months previous to the current pawn, as well as a dummy for the having pawned in the period $t'$ to $t$. The main regressor of interest is having had a FP loan in the past from $t'$ to $t$  which measures experiencing a FP contract recently. Column 1 reports the result of first stage where the supply side instrument is an indicator for the branch having had a FP available when the client showed to pawn the previous pawn. Column 2 presents the two-stage least square estimate. Columns 3 and 4 are analogous, but instead of looking clients who pawned in the 6 weeks previous, it looks at those that had pawned in the previous 12 months. We do not report the exact number of observations to keep Lender $P$ identity confidential and instead give a lower bound. 
%\textit{Do file: } \texttt{iv\_reg\_demand\_pf.do}
\end{table}

>>>>

 \documentclass[oneside,11pt]{article}

\input{preamble.tex}
%%% HELPER CODE FOR DEALING WITH EXTERNAL REFERENCES
\usepackage{xr}
\makeatletter
\newcommand*{\addFileDependency}[1]{
  \typeout{(#1)}
  \@addtofilelist{#1}
  \IfFileExists{#1}{}{\typeout{No file #1.}}
}
\makeatother

@@

@@

\pagenumbering{arabic}
\etocdepthtag.toc{mtchapter}
\etocsettagdepth{mtchapter}{subsection}
\etocsettagdepth{mtappendix}{none}

@@

% \section{Introduction}

@@

\section{Experiment} \label{Experiment}

@@

Figure \ref{reincidence} presents results of equation (\ref{basic_reg}) where the dependent variable is a dummy for the client being a repeat costumer. We define a client as a repeat costumer if, after experiencing at least 75 days of the respective treatment arm, she came back and pawned a \textit{different} piece.\footnote{Results are robust to using number of days experiencing the contract larger than 75. We know its a different piece from it having a different weight/value.}  The left most coefficient shows that the causal effect of the fee-forcing contract on repeat pawning is an increase of 5 percentage points in the probability of being a repeat costumer, this is 55\% increase on a mean re-incidence with respect to those that got the status-quo contract. This effect is not explained by clients recovering their first pawn with higher probability in the fee-forcing contract and re-pawning this same one since we make sure it is another piece (only 16\% recover their piece in the fist 75 days in the fee forcing contract). The second coefficient restricts the sample in the regression to those that had not recovered their pawn in the first 75 days and finds similar result. The third coefficient conditions on clients who recovered the pawn in both arms. The fourth coefficient focuses on the subsample who had or would have had a financial cost savings treatment effect above the median treatment effect in their first pawn. It shows that for these clients the likelihood of coming back is twice as large (although imprecise). That is, those that benefit more from the fee-forcing contract are more likely to repeat.\footnote{The second and third estimate must be interpreted with care as we are conditioning on a variable that may be affected by treatment. We view these as suggestive correlations. The fourth coefficient does not have that problem as it conditions on clients that by their pre-determined covariates are predicted to have above the median treatment effects (in both arms).} Experience with the frequent payment contract seems to be necessary as there is no effect of the monthly payment contract on repeat pawning in the first 30 or 60 days of the contract (see Figure \ref{reincidence_before} in the Appendix). %We also implemented an exit survey which clients filled when recovering their piece. Unfortunately it had low response rate (7\%), and we take its results with a grain of salt. In this survey 63\% of clients said they liked the frequent payment contract more than the status-quo one, and that it allowed them to avoid unnecessary expenses. %The coefficient on repeat pawning is just as big when we focus only 2nd pawns happening after the first was recovered (third coefficient ``fnr'').  This is consistent with \cite{Laibson2018}'s conjecture that clients could be making decisions based on experienced utility.\footnote{The third coefficient conditions on the subsample that did recover their first pawn in both arms and finds a coefficient of 4pp. This is not a causal estimate as recovery is influenced by treatment, but we found it telling that the differences were similar to the causal estimate for the full sample.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Figures}

\begin{figure}[H]
     \caption{Experiment description}
    \label{exp_description}
    \begin{center}
    \begin{subfigure}{.40\textwidth}
      \caption{Timeline of the experiment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/timeline_suc_exp_extended.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
    \caption{Experiment arms}
       \centering
      \includegraphics[width=\textwidth]{Figuras/exp_arms.PNG}
    \end{subfigure}
    \end{center}
         \scriptsize Panel (a) displays in black arrows the period covered by our administrative data: from August 6th 2012 (30 days before the experiment began) to August 13th 2013. The gray lines arrows correspond to the dates of implementation of the experiment. We finished the experiment earlier in branches 1 and 2 because we realized that we would have enough sample size with the remaining branches and save on operational costs. Panel (b) shows our 5 treatment arms: control (status quo contract), no fee-forcing, promise-forcing, choice among status quo and fee-commitment, and choice among status quo promise-commitment. Within each arm it displays the number of observations. And  for the choice groups it splits the sample size into those who chose the commitment contract (shaded blue triangle) and those that did not (un-shaded triangle).
%\textit{Do file: }  \texttt{timeline\_suc\_exp.do}
\end{figure}

@@

% APPENDIX 
\setcounter{table}{0}
\setcounter{figure}{0}
\setcounter{section}{0}
\pagenumbering{gobble}

\begin{center}
	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
	\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Isaac Meza \and Joyce Sadka \and Enrique Seira}
\end{center}

%\renewcommand{\cftparskip}{0em} % NOT NEEDED
\renewcommand\cftsecdotsep{\cftdotsep}
\renewcommand\cftsubsecdotsep{\cftnodots}
\renewcommand{\cftsecnumwidth}{6em}
 \renewcommand{\cftpnumalign}{r}
%\renewcommand{\cftsecleader}{\normalfont\cftdotfill{\cftsecdotsep}}

\renewcommand{\cftsecleader}{\cftdotfill{\cftsecdotsep}\hspace{1.8em}}
%\renewcommand{\cftsecpagefont}{20em}
%\renewcommand{\cftfignumwidth}{6em}
%\renewcommand{\cfttabnumwidth}{3.3em}

%\tableofcontents
\etocdepthtag.toc{mtappendix}
\etocsettagdepth{mtchapter}{none}
\etocsettagdepth{mtappendix}{subsection}

\setstretch{0.9}
%\renewcommand\contentsname{} % the empty name

\begingroup
\let\clearpage\relax
%\vspace{-1.5em} % the removed space. Set as appropriate
\tableofcontents
\endgroup

\newpage
\pagenumbering{arabic}
\renewcommand\thefigure{OA-\arabic{figure}}
\renewcommand\thetable{OA-\arabic{table}}
\renewcommand*{\thepage}{OA - \arabic{page}}
\renewcommand\thesection{Appendix \Alph{section}.}
\renewcommand\thesubsection{\Alph{section}.\arabic{subsection}}

\section{ Further results}
\vspace{.2in}

@@

\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}
\scriptsize{\input{./Tables/mechanism.tex}}
\end{center}

@@

\scriptsize {
\noindent This table explores treatment effects in ``intermediate variables''. Each column represents a different dependent variable in an OLS regression, and each panel represents a different treatment arm-control comparison. All regressions include fixed effects for branch, day of week fixed effects, number of pawns at the time of pawning this particular one, number of different treatment arms experienced before pawning this particular one. $R^2$ are not reported, they were less than 0.04 for all but the last column which had $R^2$'s close to 0.6. The last row shows the mean of the dependent variable for the control group. Dependent variables are as follows: Column (1) measures the number of days elapsed from the pawning date to the first payment done. Column (2) records the number of payments done within 230 days of the pawn. Column (3) is the average size of the payments for each client in pesos. Column (4) is self-reported cost to get to the branch plus the imputed loss of a whole day of salary (using the minimum wage in Mexico) multiplied by the number of visits to the branch. Column (5) measures the number of days it took to recover the pawn, conditional on recovering. The dependent variable in Column (6) is a dummy =1 if the client paid any positive amount within 230 days of the pawn. For Columns (7) and (8) the dependent variable it is the sum of total payments done within 230 days of the pawn divided by the size of the loan, but column (8) includes as regressors a dummy=1 if the client recovered her pawn, and its interaction with treatment.
}

\subsection{FOSD: fee forcing vs status quo financial cost distributions}

@@

% APPENDIX B

\newpage
\section{ Observational analysis}
\label{appendix_b}
\vspace{.2in}
\normalsize
\linespread{1.25}

@@

\vspace{.1in}
\begin{figure}[H]
        \caption{Existence of FP per branch}
    \label{variation_pf_suc}
    \begin{center}
        \centering
        \includegraphics[width=0.9\textwidth]{Figuras/active_pf_suc.pdf}
    \end{center}
     \scriptsize This Figure shows the presence of the frequent payment (FP) contract in 20 randomly chosen branches of Lender $P$ for a span of more than 4 years. A $y$ value $=1$ means that in that month the FP contract was available in that branch. 
     %\textit{Do file: }  \texttt{active\_pf\_suc.do}
\end{figure}
\vspace{.1in}

@@

\begin{table}[H]
\caption{Experience with frequent payment contract raises future demand for it}
\label{iv_pf}
\begin{center}
\footnotesize{\input{./Tables/iv_reg_demand_pf.tex}}
\end{center}
 \scriptsize
This table shows resulting estimates of variants of equation  \ref{eqn:IV} above. They regress a dummy for the client choosing a frequent payment contract (when both the traditional one and the FP are available) on whether the previous loan was under a FP contract. All columns have client, branch, and calendar month fixed effects. All of them control for the number of times the client has pawned in the 12 months previous to the current pawn, as well as a dummy for the having pawned in the period $t'$ to $t$. The main regressor of interest is having had a FP loan in the past from $t'$ to $t$  which measures experiencing a FP contract recently. Column 1 reports the result of first stage where the supply side instrument is an indicator for the branch having had a FP available when the client showed to pawn the previous pawn. Column 2 presents the two-stage least square estimate. Columns 3 and 4 are analogous, but instead of looking clients who pawned in the 6 weeks previous, it looks at those that had pawned in the previous 12 months. We do not report the exact number of observations to keep Lender $P$ identity confidential and instead give a lower bound. 
%\textit{Do file: } \texttt{iv\_reg\_demand\_pf.do}
\end{table}
